### 2023-02-06 article.tex
EOD

\begin{itemize}
  \item Code must be clean
  \item Code must be hosted
  \begin{itemize}
    \item Hosted code generated important metadata
    \item Code must be tested
    \item ...
  \end{itemize}
  \item Code must be tested
  \begin{itemize}
    \item ...
  \end{itemize}
\end{itemize}

@@

Raw code gives an indication of the quality 
of a computational experiment and several metrics are
devised to get an idea of the quality of code.

@@

@@

@@

% \paragraph{Code must be hosted to be moderately computer-friendly}
Code is sometimes published alongside a paper, 
in the form of a code hosting website.
This way of publishing code gives additional options,
both for the authors of that code, as well as its users.
This practice has increased,
with the abstracts from articles in the academic journal
'Bioinformatics' referring to such a hosted website
has increased tenfold, going from below 5 percent in 2009 
to around 50 percent in 2017 \cite{russell2018large}.

\paragraph{Example of hosted code}

@@

% \paragraph{Runnable code is the pinnacle of reproducible research}

When research truly needs to be reproducible, putting the code 
of an experiment into a container is a good solution, as it 
can stand the test of time better.
Creating such a container, however, requires more skill
that -as of today- is not rewarded,
partly as containers follow FAIR data principles only poorly.

>>>>

@@

Code gives an indication of the quality 
of a computational experiment and several metrics are
devised to get an idea of the quality of code.

\paragraph{SLOC}

@@

\paragraph{Cyclomatic complexity}

@@

\paragraph{Error handling}

@@

There exist website that are dedicated to host code.
Such so-called code hosting websites have many advantages,
both for the authors and users of the code,
over copy-pasting code in the supplementary materials in a paper.

The practice of using a code hosting websote has increased,
with the abstracts from articles in the academic journal
'Bioinformatics' referring to such a hosted website
has increased tenfold, going from below 5 percent in 2009 
to around 50 percent in 2017 \cite{russell2018large}.

\paragraph{Example of code hosting website}

@@

\paragraph{First step: publish code alongside papers}

\paragraph{Final goal: runnable code}

When research truly needs to be reproducible, putting the code 
of an experiment into a container is a good solution, as it 
can stand the test of time better.
Creating such a container, however, requires more skill
that -as of today- is not rewarded,
partly as containers follow FAIR data principles only poorly.
Runnable code is the pinnacle of reproducible research.
